---
title: "batata"
description: |
  A Toolbox for Managing R Packages Installation and Removal.
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<h1 style = "color:#24BFA5; text-align:center;">
Packages Removal
</h1>

## `fresh_start()`

__Description__
Removes all the installed R packages (including base R) within an installation directory. Particularly useful when moving from an R version to another.

__Parameters__

- `lib` (str): the directory where to remove the packages. Defaults to the first element in `.libPaths()`


## `today_packages()`

__Description__
Displays all the packages installed the day the function is called. 

__Parameters__

- `lib` (str): the directory where to display the packages. Defaults to the first element in `.libPaths()`

__Example__

```{r}
library(batata)
today_packages()
```

## `rm_today_packages()`

__Description__
Removes all the packages installed the day the function is called. 

__Parameters__

- `lib` (str): the directory where to remove the packages. Defaults to the first element in `.libPaths()`


## `yesterday_packages()`

__Description__
Displays the packages installed _yesterday_. 

__Parameters__:

- `lib` (str): the directory where to display the packages. Defaults to the first element in `.libPaths()`

__Example__

```{r}
yesterday_packages()
```

## `rm_yesterday_packages()`

__Description__
Removes all the packages installed _yesterday_.

__Parameters__

- `lib` (str): the directory where to remove the packages. Defaults to the first element in `.libPaths()`


## `since_packages()`

__Description__
Displays the packages installed according to a specific date.

__Parameters__

- `date` (str): the considered date in __yyyy-mm-dd__ format
- `position` (str): whether to display the packages installed `at` that date, `before` or `after` that date.
- `lib` (str): the directory where to display the packages. Defaults to the first element in `.libPaths()`

__Example__

```{r}
#packages installed after the first of January 2021
since_packages(date = "2021-01-01", 
               position = "after")
```


## `rm_since_packages()`

__Description__
Works similarly to `since_packages()` excepts that it removes the packages instead of displaying them. 

__Parameters__
Same as `since_packages()`

## `latest_packages()`

__Description__
Displays the latest installed packages. 

__Parameters__

- n (num): the number of the last installed packages to display. Default to n = 1, in this case it will return the last installed package.

- `lib` (str): the directory where to display the packages. Defaults to the first element in `.libPaths()`

__Example__

```{r}
# 10 latest packages installed
latest_packages(n = 10)
```

## `rm_latest_packages()`

__Description__
Works similarly to `rm_latest_packages()` excepts that it removes the packages instead of displaying them. 

__Parameters__
Same as `since_packages()`

<!-- laaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaast -->

<hr style = "border: solid 3px #FF4E5C; width:80%;">

<h1 style = "color:#24BFA5; text-align:center;">
Packages Installation 
</h1>


## `install_starred_cran()`

__Description__
Installs the latest CRAN-available R packages starred on Github. 

__Parameters__

- `github_user` (str): the Github user name
- `n` (num): the last `n` starred repositories. Defaults to 5, in which case the function will look for the last 5 starred repositories, filter R from non-R repos and install them if available on CRAN.

__Example__
The following code chunk will look at the last 10 repositories that I have starred, filter out R repositories, and install them if available on CRAN: 


```{r, eval=FALSE}
# my Github user name is 'feddelegrand7'
install_starred_cran(github_user = 'feddelegrand7', n = 10)
```

Note that if the starred repo is not available on CRAN, `install_starred_cran()` will simply ignore it.

## `install_starred_github()`

__Description__
`install_starred_github()` behaves the same way as `install_starred_cran()` except that it will install the repositories from Github (not from CRAN), so that you can install packages that are not available on CRAN.

__Parameters__

- `github_user` (str): the Github user name
- `n` (num): the last `n` starred repositories. Defaults to 5, in which case the function will look for the last 5 starred repositories, filter R from non-R repos and install them
- `upgrade` (str): whether to upgrade or not out of date packages. You can choose from 'always' or 'never'. Defaults to 'never'. For more info, see `install_github()` from the `remote` package.

__Example__
The following code chunk will look at the last five repositories that I have starred, extract R repositories (in case some starred repositories belong to another programming language) and install them:

```{r, eval=FALSE}
install_starred_github(github_user = 'feddelegrand7', 
                       n = 5, 
                       upgrade = "never")
```

## `install_most_starred()`

__Description__
Allows you the install the most starred CRAN packages that are available on Github. It takes one argument `n` which specifies the number of the most starred R packages (in descending order) that one wants to install.

__Parameters__

- `n`: the number of most starred CRAN packages (in descending order). Defaults to 10, in which case the function will look at the 10 most starred R repositories and install them if available on CRAN.


__Example__
The following code chunk will look for the 10 most starred R repositories and will install them if available on CRAN. Of course, it will ignore R repositories that are not packages, (e.g R4DS repo):

```{r, eval=FALSE}
install_most_starred(n = 10)
```


## Code of Conduct

Please note that the batata project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

