---
title: "Packages Installation"
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## `display_starred()`

__Description__
Display User's Github Starred Repositories.

__Parameters__

- `github_user` (str): the Github user name to look for
- `n` (num): the number of the last starred repositories. Defaults to 5 in which case
it will return the last 5 starred repositories. Note that if the  `onlyR` parameter
is set to TRUE, you might get a lower number of starred repos due to filtering R from
all the other languages.
- `onlyR` (lgl): whether to fetch only R repositories, Default to FALSE


```{r}
library(batata)

display_starred('hadley', n = 20, onlyR = FALSE)
```

## `install_starred_cran()`

__Description__
Installs the latest CRAN-available R packages starred on Github. 

__Parameters__

- `github_user` (str): the Github user name to look for
- `n` (num): the last `n` starred repositories. Defaults to 5, in which case the function will look for the last 5 starred repositories, filter R from non-R repos and install them if available on CRAN.

__Example__
The following code chunk will look at the last 10 repositories that I have starred, filter out R repositories, and install them if available on CRAN: 


```{r, eval=FALSE}
# my Github user name is 'feddelegrand7'
install_starred_cran(github_user = 'feddelegrand7', n = 10)
```

Note that if the starred repo is not available on CRAN, `install_starred_cran()` will simply ignore it.

## `install_starred_github()`

__Description__
`install_starred_github()` behaves the same way as `install_starred_cran()` except that it will install the repositories from Github (not from CRAN), so that you can install packages that are not available on CRAN.

__Parameters__

- `github_user` (str): the Github user name to look for
- `n` (num): the last `n` starred repositories. Defaults to 5, in which case the function will look for the last 5 starred repositories, filter R from non-R repos and install them
- `upgrade` (str): whether to upgrade or not out of date packages. You can choose from 'always' or 'never'. Defaults to 'never'. For more info, see `install_github()` from the `remote` package.

__Example__
The following code chunk will look at the last five repositories that I have starred, extract R repositories (in case some starred repositories belong to another programming language) and install them:

```{r, eval=FALSE}
install_starred_github(github_user = 'feddelegrand7', 
                       n = 5, 
                       upgrade = "never")
```

## `install_most_starred()`

__Description__
Allows you the install the most starred CRAN packages that are available on Github. It takes one argument `n` which specifies the number of the most starred R packages (in descending order) that one wants to install.

__Parameters__

- `n`: the number of most starred CRAN packages (in descending order). Defaults to 10, in which case the function will look at the 10 most starred R repositories and install them if available on CRAN.


__Example__
The following code chunk will look for the 10 most starred R repositories and will install them if available on CRAN. Of course, it will ignore R repositories that are not packages, (e.g R4DS repo):

```{r, eval=FALSE}
install_most_starred(n = 10)
```

