---
title: "Packages Removal"
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## `fresh_start()`

__Description__
Removes all the installed R packages (including base R) within an installation directory. Particularly useful when moving from an R version to another.

__Parameters__

- `lib` (str): the directory where to remove the packages. Defaults to the first element in `.libPaths()`


## `today_packages()`

__Description__
Displays all the packages installed the day the function is called. 

__Parameters__

- `lib` (str): the directory where to display the packages. Defaults to the first element in `.libPaths()`

__Example__

```{r}
library(batata)
today_packages()
```

## `rm_today_packages()`

__Description__
Removes all the packages installed the day the function is called. 

__Parameters__

- `lib` (str): the directory where to remove the packages. Defaults to the first element in `.libPaths()`


## `yesterday_packages()`

__Description__
Displays the packages installed _yesterday_. 

__Parameters__:

- `lib` (str): the directory where to display the packages. Defaults to the first element in `.libPaths()`

__Example__

```{r}
yesterday_packages()
```

## `rm_yesterday_packages()`

__Description__
Removes all the packages installed _yesterday_.

__Parameters__

- `lib` (str): the directory where to remove the packages. Defaults to the first element in `.libPaths()`


## `since_packages()`

__Description__
Displays the packages installed according to a specific date.

__Parameters__

- `date` (str): the considered date in __yyyy-mm-dd__ format
- `position` (str): whether to display the packages installed `at` that date, `before` or `after` that date.
- `lib` (str): the directory where to display the packages. Defaults to the first element in `.libPaths()`

__Example__

```{r}
#packages installed after the first of January 2021
since_packages(date = "2021-01-01", 
               position = "after")
```


## `rm_since_packages()`

__Description__
Works similarly to `since_packages()` excepts that it removes the packages instead of displaying them. 

__Parameters__
Same as `since_packages()`

## `latest_packages()`

__Description__
Displays the latest installed packages. 

__Parameters__

- n (num): the number of the last installed packages to display. Default to n = 1, in this case it will return the last installed package.

- `lib` (str): the directory where to display the packages. Defaults to the first element in `.libPaths()`

__Example__

```{r}
# 10 latest packages installed
latest_packages(n = 10)
```

## `rm_latest_packages()`

__Description__
Works similarly to `latest_packages()` excepts that it removes the packages instead of displaying them. 

__Parameters__
Same as `latest_packages()`
